---
title: "To Tidymodel or not to Tidymodel, that this the question"
subtitle: "Workshop: How to get the most out of Tidymodeling with R"
author: "Henry Baker, add group"
date: "`r Sys.Date()`" 
output: 
  ioslides_presentation:
    widescreen: true
    smaller: true
    css: styles.css 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(lattice)
library(ggplot2)
```

---

## Table of Contents

1. What is Tidymodeling?(#what_is)
2. Why Tidymodeling? Some motivations
3. Key concepts in Tidymodeling
4. What we are NOT covering
5. Workshop focus: Recipes & iterative pre-processing
6. Modeling





## Remember this?

```{r, echo=FALSE}
# non-visible 
set.seed(123) 

synthetic_data <- data.frame(
  predictor1 = rnorm(100),  
  predictor2 = rnorm(100),  
  predictor3 = rnorm(100),  
  control1 = sample(c("Yes", "No"), 100, replace = TRUE), 
  control2 = runif(100), 
  outcome = rnorm(100)  
)

synthetic_data$outcome <- with(synthetic_data, predictor1 + 2*predictor2 + rnorm(100))

```

```{r}
model <- lm(outcome ~ predictor1 + predictor2 + predictor3 + control1 + control2, data=synthetic_data)
summary(model)


- Base R equivalent: ‘R formula’


---

# R’s strength is also its greatest weakness…

One of the strengths of R is that it encourages developers to create a user interface that fits their needs. As an example, here are three common methods for creating a scatter plot of two numeric variables in a data frame called `plot_data`:


# Different Plotting Methods in R
<!-- This slide will lead into the examples. It's clean and gives a clear signal that we're about to dive into specifics. -->
# using Base R plot
```{r}
#plot(synthetic_data$x, synthetic_data$y, main="Base R Plot", pch=19, col=rgb(0.2,0.4,0.6,0.6))
```
--
## Using Lattice 
```{r}
#print(synthetic_data(y ~ x, data = plot_data, main="Lattice Plot"))
```
--
## Using ggplot2
```{r}
#ggplot(synthetic_data, aes(x = x, y = y)) + geom_point()
```
---

In these three cases, separate groups of developers devised three distinct interfaces for the same task. Each has advantages and disadvantages.

In comparison, the Python Developer’s Guide espouses the notion that, when approaching a problem:
“There should be one – and preferably only one – obvious way to do it.”

---
# A little motivation: why Tidymodels?

Just as tidyverse syntax makes our lives a whole load easier / intuitive than using base R expressions….

- **Tidyverse integration**: Built on the principles of the tidyverse, promoting consistent and user-friendly data manipulation. Familiarity with the tidyverse makes using Tidymodels seamless and consistent in data analysis and modeling workflows.

- **Consistency & workflow**: Tidymodels ensures a structured workflow for modeling, encapsulating data pre-processing, model specification, tuning, and evaluation, enhancing organization and transparency.

- **Recipes for data pre-processing**: The inclusion of the `recipes` package in Tidymodels allows structured, reproducible data pre-processing steps, beneficial for feature engineering and data transformation.

- **Model Agnosticism**: Facilitates easy swapping of different models for experimentation and selection without extensive code adjustments.

- **Hyperparameter Tuning**: Streamlined process for adjusting and finding the best model parameters.

- **Resampling & Cross-validation**: Offers resampling methods, like cross-validation and bootstrapping, essential for reliable estimations of model generalization.

- **Extensive metrics**: The `yardstick` package in Tidymodels provides a broad spectrum of evaluation metrics, simplifying model performance comparison and assessment.
---

