---
title: "I2DS Tools for Data Science Workshop 2023: Tidy modeling with tidymodels in R"
authors: "Daniyar Imanaliev, Henry Baker, Isabella Urbano Trujillo"
output: 
  html_document:
    toc: TRUE
    df_print: paged
    number_sections: FALSE
    highlight: tango
    theme: lumen
    toc_depth: 3
    toc_float: true
    css: custom.css 
    self_contained: false
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      eval = TRUE,
                      error = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      comment = NA)
```

# What is tidymodels?
Tidymodels is a collection of R packages and a framework for modeling and machine learning that follows the principles of tidy data and integrates seamlessly with the tidyverse ecosystem. It was developed to provide a consistent and organized way to perform machine learning tasks in R, making it easier for data scientists and analysts to build, evaluate, and deploy predictive models.

Install tidymodels with:
```{r, include = T}
# install.packages("tidymodels")
library(tidymodels)
```

# Why tidymodels and not other R package?


```{r}

```

